The title

### 2023-04-21 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data script.Rmd
update

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

@@

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : bookdown::word_document2 #papaja::apa6_pdf
---

```{r setup, include = FALSE}

library("papaja")
r_refs("r-references.bib")
```

@@

# prepare data (selected from questionnaire data)
demo.data <- read_excel ("./data/data_empschul_labor_lehrperson.xlsx")

@@

# changing gender female 2 = 0 
demo.data$Gender = ifelse(demo.data$Gender == 2, "0","1")

@@

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Male" = sum(Gender),
            "M Age" = round(mean(Age), 2),
            "Min Age" = min(Age),
            "Max Age" = max(Age),
            "SD Age" = round(sd(Age), 2),
            "M Exp." = round(mean(`Teaching Experience`), 2),
            "Min Exp." = min(`Teaching Experience`),
            "Max Exp." = max(`Teaching Experience`),
            "SD Exp." = round(sd(`Teaching Experience`), 2),
           )

@@

::: {#refs custom-style="Bibliography"}
:::

>>>>

---
title             : "Through the eyes of the teacher"
shorttitle        : "Visual attention in teaching and learning processes"

author: 
  - name          : "Mandy Klatt"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Dittrichring 5-7, 04109 Leipzig"
    email         : "mandy.klatt@uni-leipzig.de"
  - name          : "Dr. Gregor Kachel"
    affiliation   : "1, 2"
  - name          : "Dr. Christin Lotz"
    affiliation   : "1"
  - name          : "Prof. Dr. Anne Deiglmayr"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Leipzig University"
  - id            : "2"
    institution   : "Max-Planck University for Evolutionary Anthropology"

authornote: |
  Ethics Approval
  All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board. The authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.

  Consent to Participate
  All participants gave informed consent.

abstract: |

keywords          : "Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking"
wordcount         : "XXX"

@@

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : bookdown::word_document2
---

```{r setup, include = FALSE}
install.packages('papaja')
library("papaja")
r_refs("r-references.bib")
```

@@

# prepare data (selected from questionnaire data)
demo.data <- readxl::read_xlsx("./data/data_empschul_labor_lehrperson.xlsx")

@@

# changing gender female 2 = 1 
demo.data$Gender = ifelse(demo.data$Gender == 2, "1","0")

@@

# #filter --> 121 two times
# demo.data <-  demo.data[-c(28), ]

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Female" = sum(Gender),
            "M Age" = round(mean(Age), 2),
            "Min Age" = min(Age),
            "Max Age" = max(Age),
            "SD Age" = round(sd(Age), 2),
            "M Exp." = round(mean(`Teaching Experience`), 2),
            "Min Exp." = min(`Teaching Experience`),
            "Max Exp." = max(`Teaching Experience`),
            "SD Exp." = round(sd(`Teaching Experience`), 2),
           )

@@

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
